---
title: "Untitled"
author: "Bradford Condon"
date: "4/10/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Knitting R Markdown to Jekyll

This is a test of the Knittr package and Jekyll.

It looks like the original package for using knitr with Jekyll [here](https://github.com/yihui/knitr-jekyll) has fallen out of favor for Hugo, a GO-based static web-site generator.  Pretty cool, but let's see how easy it is to knit into Jekyll without using any packages.

###Load in some libraries and data

```{r, warning=FALSE, message=FALSE}
require(ggplot2)
require(knitr)
attach(mtcars)
```


####Do some plots

````{r}
head(mtcars)

qplot(mpg, drat, data=mtcars, color=cyl, main="mpg vs drat mtcars")

```

>Behold my beautiul plot


#####Render

Next we need to get our RMD to MD, with the image paths sorted.  To do this I'll stand on the shoulders of [chepec](https://chepec.se/2014/07/16/knitr-jekyll.html) who has implemented a solution.  I created a `_knitr` directory in my Jekyll site, and I included a `knitr` folder in my `assets` folder.  Make sure you update the necessary paths in the `render_post.r` file.

Now its a matter of simply sourcing hte file and running `KnitPost`
